Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project

### 2022-05-24 papers/main.tex
Explain convex hull constraints

@@

Costs related to unit commitment, $z_{gt}$, have been omitted for brevity.

@@

\begin{align}
    d_{nt}^{min} \leq $d_{nlt}^{L^+}$ \leq d_{nt}^{max} & \quad n \in N, \; l \in L^+, \; t \in T
    d_{nt}^{min} \leq $d_{nlt}^{L^-}$ \leq d_{nt}^{max} & \quad n \in N, \; l \in L^-, \; t \in T
\end{align}

It is possible to calculate $d_{nt}^{min}$ and $d_{nt}^{max}$ since the quantiles for $D^{L^+}$ and $D^{L^-}$ are calculated based on forecast error scenarios which \emph{are} defined at the nodal level. These limits are shown in

@@

@@

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{ccccccc}
        \toprule
        UC  & DANet & PSCD & RSL & AbsImb & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
        \midrule
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results with operating reserves but no reserve activation network constraints. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit, AbsImb = limit on absolute value of nodal imbalances}\label{tab:results_no_RANet}
\end{table}

>>>>

\section{Interaction description}

All code can be found at \href{https://github.com/junglegobs/ASoSEPOC}{https://github.com/junglegobs/ASoSEPOC}.

@@

Costs related to unit commitment, $z_{gt}$, have been omitted for brevity though they are included in the model.

@@

\begin{align}
    d_{nt}^{min} \leq d_{nlt}^{L^+} \leq d_{nt}^{max} & \quad n \in N, \; l \in L^+, \; t \in T \\
    d_{nt}^{min} \leq d_{nlt}^{L^-} \leq d_{nt}^{max} & \quad n \in N, \; l \in L^-, \; t \in T
\end{align}

It is possible to calculate $d_{nt}^{min}$ and $d_{nt}^{max}$ since the quantiles for $D^{L^+}$ and $D^{L^-}$ are calculated based on forecast error scenarios which \emph{are} defined at the nodal level. These limits are shown in Figure \ref{fig:imbalance_range}. Clearly it is simply not possible to have an imbalance on some nodes, such as Coo (the location of Belgium's pumped hydro unit). Constraining $d_{nlt}^{L^+}$ and $d_{nlt}^{L^-}$ in this way is referred to as AbsImb later on.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{../plots/nodal_imbalance_investigation/imbalance_range}
    \caption{Range of possible imbalances for all hours of day 309.\label{fig:imbalance_range}}
\end{figure}

The other possibility is to restrict $d_{nlt}^{L^+}$ and $d_{nlt}^{L^-}$ to lie within the convex hull of all imbalances. This is illustrated in 2 dimensions in Figure \ref{fig:convex_hull_tihange} for the imbalances at Tihange 1 and 2. Clearly the imbalances are highly correlated, and constraining the possible nodal imbalances to lie within the convex hull exploits this in a way that box constraints would not be able to.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{../plots/nodal_imbalance_investigation/convex_hull_TIHANGE 1_TIHANGE 2}
    \caption{Illustration of convex hull constraints on $d_{nlt}^{L^+}$ and $d_{nlt}^{L^-}$. Blue circles are imbalance scenarios, shaded area is the convex hull, $d_{nt}^{min}$ and $d_{nt}^{max}$ are the x limits for TIHANGE 1 and the y limits for TIHANGE 2. \label{fig:convex_hull_tihange}}
\end{figure}

@@

\todo[inline]{For now, see README.md}

@@

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{cccccccc}
        \toprule
        UC  & DANet & PSCD & RSL & AbsImb & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
        \midrule
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results with operating reserves but no reserve activation network constraints. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit, AbsImb = limit on absolute value of nodal imbalances}\label{tab:results_no_RANet}
\end{table}
